Effects of the body force on the evacuation dynamics

### 2020-01-29 paper.tex
correcciones menores

In Fig. \ref{flow_density} we show the flow as a function of the global density (fundamental diagram). \ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5. Each curve correspond to a different friction value (see the caption).\\

@@

To conclude this section, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks. The walls in the corridors play a critical role that prevents pedestrians from detaching from each other. This effect has consequences such as increasing the connectivity of the contact network, flattening the velocity profile (thus reducing the strain rate). If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high. This leads to a"solidification" of the crowd that makes all the pedestrians walk at almost the same velocity. The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd. \\

>>>>

@@

\subsection{Dimensionless numbers and comparison with empirical data}

Fig. \ref{flow_density} shows the flow as a function of the global density (fundamental diagram). \ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5. Each curve correspond to a different friction value (see the caption).\\

To conclude section \ref{results}, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks. The walls in the corridors play a critical role that prevents pedestrians from detaching from each other. This effect has consequences such as increasing the connectivity of the contact network, flattening the velocity profile (thus reducing the strain rate). If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high. This leads to a"solidification" of the crowd that makes all the pedestrians walk at almost the same velocity. The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd. \\
